{\helveticaitalic{Supplementary Material}}: \\ \helvetica{Xolotl: An Intuitive and Approachable Neuron \& Network Simulator in MATLAB}

### 2018-08-07 paper/supplementary/supplementary.tex
Add maximal conductances for Liu models

		\begin{center}
			\begin{tabular}{|l|r|l|}
				\hline 
				\textbf{Parameter Name} & \textbf{Value} & \textbf{Units} \\ 
				\hline 
				Membrane capacitance ("AB.Cm") & 10 & ${nF}/{mm^2}$ \\ 
				\hline 
				Surface area ("AB.A") & 0.0628 & $mm^2$ \\
				\hline
				Calcium buffering $\phi$ ("AB.phi") & 90 & $\mu M / nA$ \\
				\hline
				Calcium buffering shell volume ("AB.vol") & 0.0628 & $mm^3$ \\
				\hline 
				Fast sodium maximal conductance ("AB.NaV.gbar") & 00 & $\mu S/mm^2$ \\ 
				\hline
				Transient calcium maximal conductance ("AB.CaT.gbar") & 00 & $\mu S/mm^2$ \\ 
				\hline 
				Slow calcium maximal conductance ("AB.CaS.gbar") & 00 & $\mu S/mm^2$ \\ 
				\hline 
				Transient potassium maximal conductance ("AB.ACurrent.gbar") & 00 & $\mu S/mm^2$ \\ 
				\hline 
				Calcium-gated potassium maximal conductance ("AB.KCa.gbar") & 00 & $\mu S/mm^2$ \\ 
				\hline 
				Delayed rectifier maximal conductance ("AB.Kd.gbar") & 00 & $\mu S/mm^2$ \\ 
				\hline
				Hyperpolarization-activated maximal conductance ("AB.HCurrent.gbar") & 00 & $\mu S/mm^2$ \\ 
				\hline 
				Passive leak maximal conductance ("AB.Leak.gbar") & 00 & $\mu S/mm^2$ \\ 
				\hline 
				Sodium reversal potential ("AB.NaV.E") & 30 & $mV$ \\ 
				\hline 
				Potassium reversal potential ("AB.Kd.E") & -80 & $mV$ \\ 
				\hline
				Hyperpolarization-activated reversal potential ("AB.HCurrent.E") & -20 & $mV$ \\
				\hline
				Leak reversal potential ("AB.Leak.E") & -50 & $mV$ \\
				\hline
			\end{tabular} 
		\end{center}

@@

		\begin{center}
			\begin{tabular}{|c|c|c|c|}
				\hline
				\textbf{Presynaptic} & \textbf{Postsynaptic} & \textbf{Type} & \textbf{Maximal Conductance} ($\mu S/mm^2$) \\
				\hline
				AB & LP & Chol & 30 \\ \hline
				AB & PY & Chol & 3 \\ \hline
				AB & LP & Glut & 30 \\ \hline
				AB & PY & Glut & 10 \\ \hline
				LP & PY & Glut & 1 \\ \hline
				PY & LP & Glut & 30 \\ \hline
				LP & AB & Glut & 30 \\ \hline
			\end{tabular}
		\end{center}

>>>>

		\begin{center}
			\begin{tabular}{|l|r|l|}
				\hline 
				\textbf{Parameter Name} & \textbf{Value} & \textbf{Units} \\ 
				\hline 
				Membrane capacitance ("AB.Cm") & 10 & ${nF}/{mm^2}$ \\ 
				\hline 
				Surface area ("AB.A") & 0.0628 & $mm^2$ \\
				\hline
				Calcium buffering $\phi$ ("AB.phi") & 90 & $\mu M / nA$ \\
				\hline
				Calcium buffering shell volume ("AB.vol") & 0.0628 & $mm^3$ \\
				\hline 
				Fast sodium maximal conductance ("AB.NaV.gbar") & 1831.2 & $\mu S/mm^2$ \\ 
				\hline
				Transient calcium maximal conductance ("AB.CaT.gbar") & 22.93 & $\mu S/mm^2$ \\ 
				\hline 
				Slow calcium maximal conductance ("AB.CaS.gbar") & 27.07 & $\mu S/mm^2$ \\ 
				\hline 
				Transient potassium maximal conductance ("AB.ACurrent.gbar") & 246.02 & $\mu S/mm^2$ \\ 
				\hline 
				Calcium-gated potassium maximal conductance ("AB.KCa.gbar") & 979.94 & $\mu S/mm^2$ \\ 
				\hline 
				Delayed rectifier maximal conductance ("AB.Kd.gbar") & 610.03 & $\mu S/mm^2$ \\ 
				\hline
				Hyperpolarization-activated maximal conductance ("AB.HCurrent.gbar") & 10.1 & $\mu S/mm^2$ \\ 
				\hline 
				Passive leak maximal conductance ("AB.Leak.gbar") & 0.99045 & $\mu S/mm^2$ \\ 
				\hline 
				Sodium reversal potential ("AB.NaV.E") & 30 & $mV$ \\ 
				\hline 
				Potassium reversal potential ("AB.Kd.E") & -80 & $mV$ \\ 
				\hline
				Hyperpolarization-activated reversal potential ("AB.HCurrent.E") & -20 & $mV$ \\
				\hline
				Leak reversal potential ("AB.Leak.E") & -50 & $mV$ \\
				\hline
			\end{tabular} 
		\end{center}

@@

		\begin{center}
			\begin{tabular}{|c|c|c|r|}
				\hline
				\textbf{Presynaptic} & \textbf{Postsynaptic} & \textbf{Type} & $\bar{g}$ ($\mu S/mm^2$) \\
				\hline
				AB & LP & Chol & 30 \\ \hline
				AB & PY & Chol & 3 \\ \hline
				AB & LP & Glut & 30 \\ \hline
				AB & PY & Glut & 10 \\ \hline
				LP & PY & Glut & 1 \\ \hline
				PY & LP & Glut & 30 \\ \hline
				LP & AB & Glut & 30 \\ \hline
			\end{tabular}
		\end{center}

\section{Stability of Exponential Euler Method}

PUT FIGURE HERE
